\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.github.com/chrillebile/}{\Large Christian Bilevits}} & Date of birth: August 17th 1997\\
  \href{https://www.linkedin.com/in/christianbilevits/}{linkedin.com/in/christianbilevits} & Email : \href{mailto:christian@bilevits.com}{christian@bilevits.com}\\
  \href{https://www.github.com/chrillebile/}{github.com/chrillebile} & Mobile : +46-721-919-915 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Faculty of Engineering, Lund University}{Lund, Sweden}
      {Master of Science in Engineering, Information and Communication Engineering Technologies}{Aug. 2016 -- 2021}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {Polhemskolan}{Lund, Sweden}
      {Engineering, Specialization: Computer Science and Information Technology}{Aug. 2013 -- June 2016}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Axis Communications AB}{Lund, Sweden}
      {Student Software Engineer}{June 2018 - Present}
      \resumeItemListStart
        \resumeItem{Amazon Web Services (AWS)}
          {Worked mainly with CloudFormation, S3, CodePipeline, Athena, DynamoDB, EC2 and Lambda.}
        \resumeItem{Gerrit, Eiffel and RabbitMQ}
          {Developed a library in Java that converts Gerrit events to Eiffel events, also developed a POC service that takes messages from RabbitMQ, converts them using the library and then sends it back to RabbitMQ.}
        \resumeItem{Elastic}
          {Set up and used Elasticsearch, Logstash and Kibana.}
        \resumeItem{Flask, Django and FastAPI}
          {Solo developed a website with Python using Flask for easier usage of advanced tools in Kibana. Developed an API for sending and validating configuration files before sending to AWS S3.}
        \resumeItem{Development}
        {General automation Python scripts and Painless scripts for Elastic. Did some machine learning on their products to find anomalies in their updates before release. Developed Python and shell script plugins for retrieving diagnostic data from cameras and transforming the retrieved data. Implemented a configuration system for a large system using Go.}
      \resumeItemListEnd

    \resumeSubheading
      {Thank You Studio}{Copenhagen, Denmark}
      {Intern}{July 2015 - Aug 2015}
      \resumeItemListStart
        \resumeItem{Steelseries}
          {Created posters and other general design for Steelseries products.}
        \resumeItem{Nordisk Film}
          {Created text animations for their new introduction video.}
        \resumeItem{Tools}
          {Got to use all kinds of designer tools; Photoshop, Indesign, Maya 3D, Premiere and After Effects.}
      \resumeItemListEnd

    \resumeSubheading
      {Wayne's Coffee}{Lund, Sweden}
      {Cleaning}{Oct 2012 - Nov 2012}
      \resumeItemListStart
        \resumeItem{Cleaning}
          {Cleaning dishes and general table cleaning.}
      \resumeItemListEnd

    \resumeSubheading
      {\"OoB}{Lund, Sweden}
      {Inventory}{Oct 2011}
      \resumeItemListStart
        \resumeItem{Inventory \& Store}
          {Worked in the inventory and in store.}
      \resumeItemListEnd

    \resumeSubheading
      {Ajour Revision ApS}{Copenhagen, Denmark}
      {Intern}{Jan 2011}
      \resumeItemListStart
        \resumeItem{Accounting}
          {Accounting and general office work.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%
%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \item{
        \textbf{Languages}{: Swedish, Danish, English}
    }
   \item{
     \textbf{Programming Languages}{: Java, Python, Go, Javascript, SQL, JSON, Painless, HTML, CSS}
   }
 \resumeSubHeadingListEnd

%-----------Other-----------------
\section{Other}
  \resumeSubHeadingListStart
    \resumeSubItem{Websites}
      {Created multiple websites, including design and developed a website for Kronan Assistans AB, 2016.}
    \resumeSubItem{Telegram Bot}
      {Created a chat bot using different API's; Google, Wolfram Alpha, Wikipedia and developed an simple AI chat bot.}
    \resumeSubItem{Telegram translation}
      {Translating the application Telegram to Swedish.}
    \resumeSubItem{Google Hash Code}
      {Participated in Google Hash Code 2017 and 2021. In 2021 were my team place 303 of more than 10 000 teams. \href{https://bit.ly/3mTqDJg}{https://bit.ly/3mTqDJg}}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
